\documentclass[a4paper,oneside,english,reqno]{amsbook}
\usepackage[T1]{fontenc}
\synctex=-1
% \usepackage{xcolor}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{mathrsfs}
% \usepackage{url}
\usepackage{amstext}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{agt}
% \usepackage{rotating}
\usepackage{subcaption}

\makeindex
% \usepackage[all]{xy}
% \usepackage[unicode=true,
%  bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
%  breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=true]
%  {hyperref}
\hypersetup{pdftitle={Algebraic General Topology. Volume 1 addons},
 pdfauthor={Victor Porton},
 pdfsubject={general topology},
 pdfkeywords={algebraic general topology,quasi-uniform spaces,generalizations of proximity spaces,generalizations of nearness spaces,generalizations of uniform spaces}}

\usepackage{xr,refcount}
\externaldocument[book-]{volume-1}
\newcommand{\bookref}[1]{\ref*{book-#1}}

% Continue numbering of book.pdf
\setcounter{thm}{\getrefnumber{book-finalthm}}
\addtocounter{thm}{-1}
\AtBeginDocument{\setcounter{figure}{\getrefnumber{book-LASTFIGURE}}} % TODO

\global\long\def\Low{\operatorname{Low}}
\global\long\def\Back{\operatorname{Back}}

\begin{document}

\title{Algebraic General Topology. Volume 1 addons}

\author{Victor Porton}

\email{\href{mailto:porton@narod.ru}{porton@narod.ru}}


\urladdr{\href{http://www.mathematics21.org}{http://www.mathematics21.org}}


\date{\today}


\begin{abstract}
This file contains future addons for the free e-book ``Algebraic General
Topology. Volume 1'', which are yet not enough ripe to be included into the
book.
\end{abstract}


\keywords{algebraic general topology, quasi-uniform spaces, generalizations
of proximity spaces, generalizations of nearness spaces, generalizations
of uniform spaces}


\subjclass[2000]{54J05, 54A05, 54D99, 54E05, 54E15, 54E17, 54E99}

\maketitle

\tableofcontents{}

\chapter{About this document}

This file contains future addons for the free e-book ``Algebraic General
Topology. Volume 1'', which are yet not enough ripe to be included into the
book.

Theorem (including propositions, conjectures, etc.) numbers in this document start from the last theorem number
in the book plus one. Theorems references inside this document are hyperlinked, but references
to theorems in the book are not hyperlinked (because PDF viewer Okular 0.20.2 does not support
Backward button after clicking a cross-document reference, and thus I want to avoid clicking such links).

\include{chap-applications}
\include{chap-limit-more}
\include{chap-fcd-rld-gal}
\include{chap-boolean-fcd}
\include{chap-interior}
\include{chap-pf-funcoid-filt}
\include{chap-sides}
\include{chap-backward}
\include{chap-quasiatoms}
\include{chap-cauchy}
\include{chap-tgroups}
\include{chap-micro}
\include{chap-connected2}
\include{chap-rels-are-fcd}
\include{chap-manifold}

% \printindex{}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
