\chapter{Unfixed objects}

\section{The lattice of unfixed filters}

\begin{thm}
Every nonempty set of unfixed filters has an infimum.
\end{thm}

\begin{proof}
Theorem~\bookref{filt-meet-form}.
\end{proof}

\begin{thm}
Every bounded above set of unfixed filters has a supremum.
\end{thm}

\begin{proof}
Theorem~\bookref{join-filt-gen} for nonempty sets of unfixed
filters. The join $\bigsqcup\emptyset=[\bot]$ for the
least filter~$\bot$ on an arbitary small set.
\end{proof}

\begin{cor}
Every small set of unfixed filters has a supremum.
\end{cor}

\begin{proof}
Let~$S$ be a small set of unfixed filters. ??
\end{proof}

\begin{obvious}
The poset of unfixed filters is bounded below (but not above).
\end{obvious}

\begin{prop}
The set of unfixed filters forms a co-brouwerian (and thus
distributive) lattice.
\end{prop}

\begin{proof}
Corollary~\bookref{filt-also-distr}.
\end{proof}

\section{Principal unfixed filters}

\begin{defn}
\emph{Principal} unfixed filter is an unfixed filter
corresponding to a principal filter on the poset of all small
sets.
\end{defn}

\begin{defn}
The \emph{filtrator of unfixed filters} is the filtrator
whose base are unfixed filters and whose core are principal
unfixed filters.
\end{defn}

We will equate principal unfixed filters with corresponding
sets.

\begin{thm}
If we add principal filters on~$B$, principal filters on
the poset of small sets containing~$B$, and above defined
principal unfixed filters corresponding to them to
appropriate nodes of the diagram~\bookref{unfix-dia}, then
the diagram turns into a commutative diagram of isomorphisms
between filtrators. (I will not draw the modified diagram to
be brief.)

Every arrow of this diagram is an isomorphism between
filtrators, every cycle in the diagram is identity.
\end{thm}

\begin{proof}
We need to prove only that principal filters on~$B$ and
principal filters on the poset of small sets containing~$B$
correspond to each other by the isomorphisms of the diagram.
But that's obvious.
\end{proof}

\begin{obvious}
The filtrator of unfixed filters is a primary filtrator.
\end{obvious}

\begin{obvious}
The filtrator of unfixed filters is down-aligned.
\end{obvious}

\begin{prop}
The filtrator of unfixed filters is
\begin{enumerate}
\item filtered;
\item with join-closed core.
\end{enumerate}
\end{prop}

\begin{proof}
Theorem~\bookref{semifilt-joinclosed}.
\end{proof}

\begin{prop}
The filtrator of unfixed filters is with binarily meet-closed core.
\end{prop}

\begin{proof}
Corollary~\bookref{f-meet-closed}.
\end{proof}

\begin{prop}
The filtrator of unfixed filters is with separable core.
\end{prop}

\begin{proof}
Theorem~\bookref{when-sep-core}.
\end{proof}

\fxnote{Properties the filtrator of unfixed filters
(stopped at ``Core part'').}

\section{Categories with embeddings}

\begin{note}
This section in not used below, it is just to feed your intuition.
\end{note}

The following generalizes the well known concept of embedding function $A
\hookrightarrow B$ for from a set $A$ to a set $B$ where $A \subseteq B$.

I will set that the unique morphism from an object $A$ to an object $B$ of a
thin category is equal to the pair $(A , B)$.

\begin{defn}
  A \emph{category with embeddings of objects} is a dagger category with a
  preorder of the set of objects together with a functor $\hookrightarrow$ (we
  will denote applying this functor to the object $(A , B)$ as $A
  \hookrightarrow B$.) such that:
  \begin{itemize}
    \item $\hookrightarrow$ is an identity on objects.
    
    \item Every $A \hookrightarrow B$ is a monomorphism.
    
    \item $(A \hookrightarrow B)^{\dagger} \circ (A \hookrightarrow B) = 1_A$.
  \end{itemize}
\end{defn}

\begin{obvious}
$A\hookrightarrow B$ is defined when $(A , B)$ is a morphism of the preorder
that is when $A \sqsubseteq B$.
\end{obvious}

\begin{obvious}
$A \hookrightarrow B : A \rightarrow B$ when $A \sqsubseteq B$.
\end{obvious}

\begin{prop}
  $A \hookrightarrow A = 1_A$.
\end{prop}

\begin{proof}
  Because $(A , A)$ is an identity morphism and $\hookrightarrow$ preserves
  identities.
\end{proof}

\begin{prop}
  $(B \hookrightarrow C) \circ (A \hookrightarrow B) = A \hookrightarrow C$
  whenever $A \sqsubseteq B \sqsubseteq C$.
\end{prop}

\begin{proof}
  $(B \hookrightarrow C) \circ (A \hookrightarrow B) = \hookrightarrow (B , C)
  \circ \hookrightarrow (A , B) = \hookrightarrow ((B , C) \circ (A , B)) =
  \hookrightarrow (A , C) = A \hookrightarrow C$.
\end{proof}

\section{\texorpdfstring{Categories under $\mathbf{Rel}$}{Categories under Rel}}

\begin{defn}
  The $\mathbf{Rel}$-morphism $\mathcal{E}^{A,B}$
  (\emph{restriction-embedding}) is defined by the formula: $\mathcal{E}^{A,B}
  = (A , B , \id_{A \cap B})$.
  
  When $A$ is clear from context, I will denote it just as $\mathcal{E}^B$.
\end{defn}

\begin{obvious}
If $A \subseteq B$ then $\mathcal{E}^{A,B}$ is an embedding $A \hookrightarrow B
= (A , B , \id_A)$.
\end{obvious}

\begin{obvious}
If $A \supseteq B$ then $\mathcal{E}^{A,B} = (A , B ,
\id_B)$.
\end{obvious}

\begin{obvious}
$\mathcal{E}^{A,A} = 1^{\mathbf{Rel}}_A$.
\end{obvious}

\begin{obvious}
$(\mathcal{E}^{A,B})^{- 1} = \mathcal{E}^{B,A}$.
\end{obvious}

\begin{defn}
\emph{Dagger functor} between two dagger categories is a functor between
these categories, which commutes with the daggers.
\fxwarning{Clearer wording.}
\end{defn}

\begin{defn}
\emph{Category under $\mathbf{Rel}$} is a pair $(C , \uparrow)$
where $C$ is a category whose objects are small sets and $\uparrow$ is an
identity-on-objects functor $\mathbf{Rel} \rightarrow C$. I call
$\uparrow$ \emph{up-arrow functor}.
\end{defn}

\begin{defn}
  \emph{Dagger category under $\mathbf{Rel}$} is a pair $(C ,
  \uparrow)$ where $C$ is a dagger category whose objects are small sets and
  $\uparrow$ is a dagger identity-on-objects functor $\mathbf{Rel}
  \rightarrow C$.
\end{defn}

\begin{defn}
  $\mathcal{E}_{\mathcal{C}}^{A,B} = \uparrow \mathcal{E}^{A,B}$. In
  other words, $\mathcal{E}_{\mathcal{C}} = \uparrow \circ \mathcal{E}$.
  
  When $A$ is clear from context, I will denote it just as $\mathcal{E}_{\mathcal{C}}^B$.
\end{defn}

\begin{prop}
  $\mathcal{E}_{\mathcal{C}}^{A,A} = 1_{\mathcal{C}}^A$.
\end{prop}

\begin{proof}
  $\mathcal{E}_{\mathcal{C}}^{A,A} = \uparrow \mathcal{E}^{A,A} =
  \uparrow 1_{\mathbf{Rel}} = 1_{\mathcal{C}}^A$.
\end{proof}

\begin{prop}
  If $f : X \rightarrow Y$ is a $\mathbf{Rel}$-morphism and
  $\im f = A \subseteq Y$ then
  \[ \mathcal{E}^{A,Y} \circ \mathcal{E}^{Y,A} \circ f = f. \]
\end{prop}

\begin{proof}
  $\mathcal{E}^{A,Y} \circ \mathcal{E}^{Y,A} \circ f = \id_A
  \circ f = f$.
\end{proof}

\begin{cor}
  If $f : X \rightarrow Y$ is a morphism of a category under
  $\mathbf{Rel}$ and $\im f = A \subseteq Y$, then
  \[ \mathcal{E}_{\mathcal{C}}^{A,Y} \circ \mathcal{E}_{\mathcal{C}}^{Y,A}
  \circ \uparrow f = \uparrow f. \]
\end{cor}

\begin{prop}
  ~  
  \begin{enumerate}
    \item If $A \subseteq B$ then $\mathcal{E}_{\mathcal{C}}^{A,B}$ is a
    monomorphism.
    
    \item If $A \supseteq B$ then $\mathcal{E}_{\mathcal{C}}^{A,B}$ is a
    epimorphism.
  \end{enumerate}
\end{prop}

\begin{proof}
  We'll prove only the first as the second is dual.
  
  Let $\mathcal{E}_{\mathcal{C}}^{A,B} \circ f = \mathcal{E}^{A,B} \circ g$. Then
  $\mathcal{E}^{B,A} \circ \mathcal{E}_{\mathcal{C}}^{A,B}
  \circ f = \mathcal{E}_{\mathcal{C}}^{B,A} \circ \mathcal{E}_{\mathcal{C}}^{A,B} \circ g$;
  $1^A \circ f = 1^A \circ g$; $f = g$.
\end{proof}

\begin{prop}
  $\mathcal{E}^{B,C} \circ \mathcal{E}^{A,B} = \mathcal{E}^{A,C}$
  iff $B \supseteq A \cap C$ (for every sets $A$, $B$, $C$).
\end{prop}

\begin{proof}
  $\mathcal{E}^{B,C} \circ \mathcal{E}^{A,B} = \mathcal{E}^{A,C}$
  is equivalent to:
  
  $(B , C , \id_{B \cap C}) \circ (A , B , \id_{A \cap B}) = (A ,
  C , \id_{A \cap C})$;
  
  $(A , C , \id_{A \cap B \cap C}) = (A , C , \id_{A \cap C})$;
  
  $A \cap B \cap C = A \cap C$;
  
  $B \supseteq A \cap C$.
\end{proof}

\begin{cor}
  $\mathcal{E}^{B,C} \circ \mathcal{E}^{A,B} = \mathcal{E}_{\mathcal{C}}^{A,C}$ if
  $B \supseteq A \cap C$ (for every sets $A$, $B$, $C$).
\end{cor}

\begin{defn}
  \emph{Partially ordered dagger category under $\mathbf{Rel}$} is
  a category which is both a partially ordered dagger category and a category
  under $\mathbf{Rel}$ such that $\uparrow \circ f^{- 1} = (\uparrow
  \circ f)^{\dagger}$ and $A \sqsubseteq B \Rightarrow \uparrow A \sqsubseteq
  \uparrow B$.
\end{defn}

\begin{prop}
  $(\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} = \mathcal{E}_{\mathcal{C}}^{B,A}$ for a dagger category under
  $\mathbf{Rel}$.
\end{prop}

\begin{proof}
  $(\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} = (\uparrow \mathcal{E}^{A,B})^{\dagger} = \uparrow (\mathcal{E}^{A,B})^{- 1} =
  \uparrow \mathcal{E}^{B,A} = \mathcal{E}_{\mathcal{C}}^{B,A}$.
\end{proof}

\begin{prop}
  For a partially ordered dagger category $\mathcal{C}$ under
  $\mathbf{Rel}$ we have $\mathcal{E}_{\mathcal{C}}^{A,B}$ is:
  \begin{enumerate}
    \item monovalued;
    
    \item injective;
    
    \item entirely defined if $A \subseteq B$;
    
    \item surjective if $B \subseteq A$.
  \end{enumerate}
\end{prop}

\begin{proof}
  ~
  \begin{enumerate}
    \item $\mathcal{E}^{A,B} \circ \mathcal{E}^{B,A} \sqsubseteq
    1^{\mathbf{Rel}}_B$; $\mathcal{E}^{A,B} \circ (\mathcal{E}^{A,B})^{- 1} \sqsubseteq 1^{\mathbf{Rel}}_B$;
    $\mathcal{E}_{\mathcal{C}}^{A,B} \circ (\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} \sqsubseteq 1^{\mathcal{C}}_B$.
    
    \item $\mathcal{E}^{B,A} \circ \mathcal{E}^{A,B} \sqsubseteq
    1^{\mathbf{Rel}}_A$; $(\mathcal{E}^{A,B})^{- 1} \circ \mathcal{E}^{A,B} \sqsubseteq 1^{\mathbf{Rel}}_A$;
    $(\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} \circ \mathcal{E}^{A,B} \sqsubseteq 1^{\mathcal{C}}_A$.
    
    \item $\mathcal{E}^{B,A} \circ \mathcal{E}^{A,B} \sqsupseteq
    1^{\mathbf{Rel}}_A$; $(\mathcal{E}^{A,B})^{- 1} \circ \mathcal{E}^{A,B} \sqsupseteq 1^{\mathbf{Rel}}_A$;
    $(\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} \circ \mathcal{E}_{\mathcal{C}}^{A,B} \sqsupseteq 1^{\mathcal{C}}_A$.
    
    \item $\mathcal{E}^{A,B} \circ \mathcal{E}^{B,A} \sqsupseteq
    1^{\mathbf{Rel}}_A$; $\mathcal{E}^{A,B} \circ (\mathcal{E}^{A,B})^{- 1} \sqsupseteq 1^{\mathbf{Rel}}_A$;
    $\mathcal{E}_{\mathcal{C}}^{A,B} \circ (\mathcal{E}_{\mathcal{C}}^{A,B})^{\dagger} \sqsupseteq 1^{\mathcal{C}}_A$.
  \end{enumerate}
\end{proof}

\section{Rectangular embedding-restriction}

\begin{defn}
  $\iota_{B_0, B_1} f = \mathcal{E}_{\mathcal{C}}^{B_1} \circ f \circ
  (\mathcal{E}_{\mathcal{C}}^{B_0})^{-1}$ for $f \in
  \Hom_{\mathcal{C}} (A_0 , A_1)$.
\end{defn}

For brevity $\iota_B f = \iota_{B, B} f$.

\begin{prop}
  $\iota_{\Src f, \Dst f} f = f$.
\end{prop}

\begin{proof}
  $\iota_{\Src f, \Dst f} f = \mathcal{E}_\mathcal{C}^{\Dst f} \circ f \circ \mathcal{E}_\mathcal{C}^{\Src f} =
  1_{\mathcal{C}}^{\Dst f} \circ f \circ 1_{\mathcal{C}}^{\Src f} = f$.
\end{proof}

\begin{prop}
  The function $\iota_{B_0, B_1} |_{f \in \Hom_{\mathcal{C}} (A_0 ,
  A_1)}$ is injective, if $A_0 \subseteq B_0 \wedge A_1 \subseteq B_1$.
\end{prop}

\begin{proof}
  Because $\mathcal{E}_{\mathcal{C}}^{A_1,B_1}$ is a monomorphism and $\mathcal{E}_{\mathcal{C}}^{A_0,B_0}$ is an epimorphism.
\end{proof}

\begin{prop}
  $\iota_{C_0, C_1} \iota_{B_0, B_1} f = \iota_{C_0, C_1} f$ for $B_0
  \supseteq A_0 \cap C_0$, $B_1 \supseteq A_1 \cap C_1$ and $f : A_0
  \rightarrow A_1$.
\end{prop}

\begin{proof}
  $\iota_{C_0, C_1} \iota_{B_0, B_1} f = \mathcal{E}_{\mathcal{C}}^{B_1,C_1}
  \circ \mathcal{E}_{\mathcal{C}}^{A_1,B_1} \circ f \circ \mathcal{E}_{\mathcal{C}}^{B_0,A_0} \circ
  \mathcal{E}_{\mathcal{C}}^{C_0,B_0} = \mathcal{E}_{\mathcal{C}}^{A_1,C_1} \circ f \circ \mathcal{E}_{\mathcal{C}}^{C_0,A_0} =
  \iota_{C_0,C_1} f$.
\end{proof}

\begin{prop}
  Let $f : A_0 \rightarrow A_1$ and $g : A_1 \rightarrow A_2$ and $A_1
  \subseteq B_1$. Then $\iota_{B_0, B_2} (g \circ f) = \iota_{B_1, B_1} g
  \circ \iota_{B_0, B_1} f$.
\end{prop}

\begin{proof}
  $\iota_{B_0, B_2} (g \circ f) = \mathcal{E}_{\mathcal{C}}^{A_2,B_2}
  \circ (g \circ f) \circ \mathcal{E}_{\mathcal{C}}^{B_0,A_0} = \mathcal{E}_{\mathcal{C}}^{A_2,B_2} \circ g \circ \id_{A_1} \circ f
  \circ \mathcal{E}_{\mathcal{C}}^{B_0,A_0} = \mathcal{E}_{\mathcal{C}}^{A_2,B_2} \circ g \circ \mathcal{E}^{B_1,A_1}
  \circ \mathcal{E}^{A_1,B_1} \circ f \circ \mathcal{E}_{\mathcal{C}}^{B_0,A_0} = \iota_{B_1, B_1} g \circ \iota_{B_0,
  B_1} f$.
\end{proof}

\section{\texorpdfstring{Examples of partially ordered dagger categories under
$\mathbf{Rel}$}{Examples of partially ordered dagger categories under Rel}}

\subsection{\texorpdfstring{Category $\mathbf{Rel}$}{Category Rel}}

Category $\mathbf{Rel}$ with the identity up-arrow functor to itself
and ``reverse relation'' as the dagger is an obvious example of a partially
ordered dagger category under $\mathbf{Rel}$.

\begin{prop}
  $\iota_{A, B} f = (A , B , \GR f \cap (A \times B))$.
\end{prop}

\begin{proof}
  $\iota_{A, B} f = \mathcal{E}^{B} \circ f \circ (\mathcal{E}^{A})^{-1} = (A , B , \GR f \cap (A \times B))$.
\end{proof}

\subsection{\texorpdfstring{Category $\mathsf{FCD}$}{Category FCD}}

Category $\mathsf{FCD}$ with the up-arrow functor
$\uparrow^{\mathsf{FCD}}$ and ``reverse funcoid'' as the dagger is a
partially ordered dagger category under $\mathbf{Rel}$.

\begin{prop}
  $\mathcal{E}_{\mathsf{FCD}}^{A,B} = (A , B , \lambda \mathcal{X}
  \in \mathfrak{F} (A) : \mathcal{X} \div B , \lambda \mathcal{Y} \in
  \mathfrak{F} (B) : \mathcal{Y} \div A)$ for objects $A \subseteq B$ of
  $\mathsf{FCD}$.
\end{prop}

\begin{proof}
  $\langle \mathcal{E}_{\mathsf{FCD}}^{A,B} \rangle \mathcal{X} =
  \bigsqcap \setcond{ \langle \mathcal{E}_{\mathsf{FCD}}^{A,B}
  \rangle^{\ast} X }{ X \in \mathcal{X} } =
  \bigsqcap \setcond{ \uparrow^B  \langle \mathcal{E}^{A,B} \rangle X
  }{ X \in \mathcal{X} } = \bigsqcap \setcond{
  \uparrow^B  (X \cap A \cap B) }{ X \in \mathcal{X}
  } = \bigsqcap \setcond{ \uparrow^B  (X \cap B) }{
  X \in \mathcal{X} } = \mathcal{X} \div B$.
  
  Rest follows from symmetry.
\end{proof}

\begin{prop}
  ~
  \begin{enumerate}
    \item $\langle \mathcal{E}_{\mathsf{FCD}}^{A,B} \rangle^{\ast} X
    = \uparrow^B X$ for every $X \in \subsets A$ if $A \subseteq B$.
    
    \item $\langle \mathcal{E}_{\mathsf{FCD}}^{B,A} \rangle^{\ast}
    Y = \uparrow^A (Y \cap A)$ for every $Y \in \subsets B$ if $A \subseteq
    B$.
  \end{enumerate}
\end{prop}

\begin{proof}
  By definition of principal funcoid.
\end{proof}

\subsection{\texorpdfstring{Category $\mathsf{RLD}$}{Category RLD}}

Category $\mathsf{RLD}$ with the up-arrow functor
$\uparrow^{\mathsf{RLD}}$ and ``reverse reloid'' as the dagger is a
partially ordered dagger category under $\mathbf{Rel}$.

\begin{obvious}
$\mathcal{E}_{\mathsf{RLD}}^{A,B} = \uparrow^{\mathsf{RLD} (A ,
B)} \id_{A \cap B}$.
\end{obvious}

\begin{defn}
  $f \div (A \times B) = (A , B , (\GR f) \div (A \times B))$ for every
  reloid $f$.
\end{defn}

\begin{prop}
  $\iota_{A, B} f = f \div (A \times B)$.
\end{prop}

\begin{proof}
  $\iota_{A, B} f = \mathcal{E}_{\mathsf{RLD}}^{B}
\circ f \circ (\mathcal{E}_{\mathsf{RLD}}^{A})^{-1} =
\bigsqcap \setcond{ \uparrow^{\mathsf{RLD}} (\mathcal{E}^{B} \circ F \circ (\mathcal{E}^{A})^{-1}
}{ F \in \GR f } = \bigsqcap \setcond{
\uparrow^{\mathsf{RLD}} (F \cap (A \times B))}
{F \in \GR f } = f \div (A \times B)$.

\fxwarning{Filters on cartesian products vs reloids.}
\end{proof}

\subsection{Some isomorphisms}

\begin{prop}
  $\setcond{ (\mathcal{A} \div A , \mathcal{A} \sqcap A) }{
  \mathcal{A} \in \mathfrak{F} (U) }$ is a function and
  moreover is an order isomorphism for a set $A \subseteq U$.
\end{prop}

\begin{proof}
  $\mathcal{A} \div A$ and $\mathcal{A} \sqcap A$ are determined by each other
  by the following formulas:
  \[ \mathcal{A} \div A = (\mathcal{A} \sqcap A) \div A \quad
     \text{and} \quad \mathcal{A} \sqcap A = (\mathcal{A} \div A) \div
     \Base (\mathcal{A}) . \]
  Prove the formulas: $(\mathcal{A} \sqcap A) \div A = \bigsqcap \setcond{
  \uparrow^A (X \cap A) }{ X \in \mathcal{A} \sqcap A
  } = \bigsqcap \setcond{ \uparrow^A (X \cap A) }{
  X \in \mathcal{A} } = \mathcal{A} \div A$.
  
  $(\mathcal{A} \div A) \div \Base (\mathcal{A}) = \bigsqcap \setcond{
  \uparrow^A (X \cap A) }{ X \in \mathcal{A} }
  \div \Base (\mathcal{A}) = \bigsqcap \setcond{ \uparrow^{\Base
  (\mathcal{A})} (Y \cap \Base (\mathcal{A})) }{
  Y \in \bigsqcap \setcond{ \uparrow^A (X \cap A) }{
  X \in \mathcal{A} } } = \text{(by properties of
  filter bases)} = \bigsqcap \setcond{ \uparrow^{\Base (\mathcal{A})} (X
  \cap A \cap \Base (\mathcal{A})) }{ X \in
  } = \bigsqcap \setcond{ \uparrow^{\Base
  (\mathcal{A})} (X \cap A) }{ X \in \mathcal{A}
  } = \mathcal{A} \sqcap A$.
  
  That this defines a bijection, follows from $\mathcal{A} \div A \sim
  \mathcal{A} \sqcap A$ what easily follows from the above formulas.
\end{proof}

\begin{prop}
  $\setcond{ (\iota_{X, Y} f , \id^{\mathbf{Rel}}_Y \circ f \circ
  \id^{\mathbf{Rel}}_X) }{ f \in
  \mathbf{Rel} (A , B) }$ is a function and moreover is an
  (order and semigroup) isomorphism, for sets $X \subseteq \Src f$, $Y
  \subseteq \Dst f$.
\end{prop}

\begin{proof}
  $\iota_{X, Y} f = (X , Y , \GR f \cap (X \times Y))$;
  $\id^{\mathbf{Rel}}_Y \circ f \circ
  \id^{\mathbf{Rel}}_X = (\Src f , \Dst f ,
  \GR f \cap (X \times Y))$. The isomorphism (both order and semigroup)
  is evident.
\end{proof}

\begin{prop}
  $\setcond{ (\iota_{X, Y} f , \id^{\mathsf{FCD}}_Y
  \circ f \circ \id^{\mathsf{FCD}}_X) }{
  f \in \mathsf{FCD} (A , B) }$ is a function and moreover is an
  (order and semigroup) isomorphism, for sets $X \subseteq \Src f$, $Y
  \subseteq \Dst f$.
\end{prop}

\begin{proof}
  From symmetry it follows that it's enough to prove that $\setcond{ \left(
  \mathcal{E}^Y \circ f , \id^{\mathsf{FCD}}_Y \circ f \right)
  }{ f \in \mathsf{FCD} (A , B) }$ is a
  function and moreover is an (order and semigroup) isomorphism, for a set $Y
  \subseteq \Dst f$.
  
  Really, $\setcond{ (\langle \mathcal{E}^Y \rangle x , \langle
  \id^{\mathsf{FCD}}_Y \rangle x) }{ x
  \in \Dst f } = \setcond{ (x \div Y , x \sqcap Y) }{
  x \in \Dst f }$ is an order isomorphism by proved
  above. This implies that $\setcond{ \left( \mathcal{E}^Y \circ f ,
  \id^{\mathsf{FCD}}_Y \circ f \right) }{
  f \in \mathsf{FCD} (A , B) }$ is an isomorphism
  (both order and semigroup).
\end{proof}

\begin{prop}
  $\setcond{ (\iota_{X, Y} f , \id^{\mathsf{RLD}}_Y \circ f \circ
  \id^{\mathsf{RLD}}_X) }{ f \in
  \mathsf{RLD} (A , B) }$ is a function and moreover is an
  (order and semigroup) isomorphism, for sets $X \subseteq \Src f$, $Y
  \subseteq \Dst f$.
\end{prop}

\begin{proof}
  $\iota_{X, Y} f = (X , Y , (\up f) \div (X \times Y))$;
  $\id^{\mathsf{RLD}}_Y \circ f \circ
  \id^{\mathsf{RLD}}_X = (\Src f , \Dst f ,
  (\up f) \sqcap (X \times Y))$. They are order isomorphic by proved
  above.
  
  $\iota_{Y, Z} g \circ \iota_{X, Y} f =\mathcal{E}^Z \circ g \circ
  (\mathcal{E}^Y)^{- 1} \circ \mathcal{E}^Y \circ f \circ (\mathcal{E}^X)^{-
  1} =\mathcal{E}^Z \circ g \circ \id^{\mathsf{RLD}}_Y \circ
  \id^{\mathsf{RLD}}_Y \circ f \circ (\mathcal{E}^X)^{- 1}$
  because $(\mathcal{E}^Y)^{- 1} \circ \mathcal{E}^Y =
  \id^{\mathbf{Rel}}_Y = \id^{\mathbf{Rel}}_Y
  \circ \id^{\mathbf{Rel}}_Y$. Thus by proved above
  \[ \setcond{ (\iota_{Y, Z} g \circ \iota_{X, Y} f ,
     \id^{\mathsf{RLD}}_Z \circ g \circ
     \id^{\mathsf{RLD}}_Y \circ \id^{\mathsf{RLD}}_Y
     \circ f \circ \id^{\mathsf{RLD}}_X) }{
     f \in \mathsf{RLD} (A , B) } \]
  is a bijection.
\end{proof}

\fxnote{Research the semigroups (Wikipedia) of funcoids and
reloids.}
