\chapter{Pointfree funcoids as a generalization of frames}

I define an injection from the set of frames to the set of pointfree endo-funcoids.

This article is a rough partial draft of a future longer writing.

\section{Definitions}

\subsection{Pointfree funcoid induced by a co-frame}

Let $\mathfrak{L}$ is a co-frame.

We will define pointfree funcoid $\Uparrow \mathfrak{L}$.

Let $\mathcal{B} (\mathfrak{L})$ is a boolean lattice whose co-subframe
$\mathfrak{L}$ is. (That this mapping exists follows from
{\cite{stone-spaces}}, page 53.) There may be probably more than one such
mapping, but we just choose one $\mathcal{B}$ arbitrarily.

Define $\cl (A) = \bigsqcap \left\{ X \in \mathfrak{L} \hspace{1em} |
\hspace{1em} X \sqsupseteq A \right\}$.

Here $\bigsqcap$ can be taken on either $\mathfrak{L}$ or $\mathcal{B}
(\mathfrak{L})$ as they are the same.

\begin{obvious}
  $\cl \in \mathfrak{L}^{\mathcal{B} (\mathfrak{L})}$.
\end{obvious}

$\cl (A \sqcup B) = \bigsqcap \left\{ X \in \mathfrak{L} \hspace{1em} |
\hspace{1em} X \sqsupseteq A \sqcup B \right\} = \bigsqcap \left\{ X \in
\mathfrak{L} \hspace{1em} | \hspace{1em} X \sqsupseteq A, X \sqsupseteq B
\right\} = \bigsqcap \left\{ X_1 \sqcup X_2 \hspace{1em} | \hspace{1em} X_1
\sqsupseteq A, X_2 \sqsupseteq B \right\} = \bigsqcap \left\{ X_1 \hspace{1em}
| \hspace{1em} X_1 \sqsupseteq A \right\} \sqcup \bigsqcap \left\{ X_2
\hspace{1em} | \hspace{1em} X_2 \sqsupseteq B \right\} = \cl A \sqcup
\cl B$.

$\cl 0 = 0$ is obvious.

Hence we are under conditions of the theorem 14.26 in my book.

So there exists a unique pointfree endo-funcoid $\Uparrow \mathfrak{L} \in
\mathsf{FCD} (\mathfrak{F} (\mathcal{B} (\mathfrak{L})) , \mathfrak{F}
(\mathcal{B} (\mathfrak{L})))$ such that
\[ \langle \Uparrow \mathfrak{L} \rangle \mathcal{X} = \bigsqcap^{\mathfrak{F}
   (\mathcal{B} (\mathfrak{L}))} \langle \cl \rangle
   \up^{\text{$(\mathfrak{F} (\mathcal{B} (\mathfrak{L})) , \mathfrak{P}
   (\mathcal{B} (\mathfrak{L})))$}}  \mathcal{X} \]
for every filter $\mathcal{X} \in \mathfrak{F} (\mathcal{B} (\mathfrak{L}))$.

\subsection{Co-frame induced by a pointfree funcoid}

The co-frame $\Downarrow f$ for some pointfree endo-funcoids $f$ will be
defined to be the reverse of $\Uparrow$. See below for exact meaning of being
reverse.

Let restore the co-frame $\mathfrak{L}$ from the pointfree funcoid $\Uparrow
\mathfrak{L}$.

Let poset $\Downarrow f$ for every pointfree funcoid $f$ is defined by the
formula:
\[ \Downarrow f = \left\{ X \in Z (\Ob f) \hspace{1em} | \hspace{1em}
   \supfun{f} X = X \right\} . \]
\begin{rem}
  It seems that $\Downarrow$ is \emph{not} a monovalued function from
  $\mathsf{pFCD}$ to $\Ob (\mathbf{Frm})$.
\end{rem}

\subsection{Isomorphism of co-frames through pointfree funcoids}

\begin{rem}
  $\mathfrak{P} (\mathcal{B} (\mathfrak{L})) = Z (\mathfrak{F} (\mathcal{B}
  (\mathfrak{L})))$ (theorem 4.137 in {\cite{volume-1}}).
\end{rem}

\begin{thm}
  $\mathfrak{L} \mapsto \Downarrow \Uparrow \mathfrak{L}$ (where
  $\mathfrak{L}$ ranges all small frames) is an order isomorphism.
\end{thm}

\begin{proof}
  Let $A' \in \Downarrow \Uparrow \mathfrak{L}$. Then there exists $A \in
  \mathcal{B} (\mathfrak{L})$ such that $A' = \uparrow^{\mathcal{B}
  (\mathfrak{L})} A$.
  
  $\supfun{f} A' = \uparrow^{\mathcal{B} (\mathfrak{L})} \cl A$.
  
  $\supfun{f} A' = A'$ that is $\uparrow^{\mathcal{B} (\mathfrak{L})}
  \cl A = A' = \uparrow^{\mathcal{B} (\mathfrak{L})} A$. So $\cl A
  = A$ and thus $A \in \mathfrak{L}$.
  
  Let now $A \in \mathfrak{L}$. Then take $A' = \uparrow^{\mathcal{B}
  (\mathfrak{L})} A$. We have $\supfun{f} A' = \cl A =
  \uparrow^{\mathcal{B} (\mathfrak{L})} A = A'$. So $A' \in \Downarrow
  \Uparrow \mathfrak{L}$.
  
  We have proved that it is a bijection.
  
  Because $A$ and $A'$ are related by the equation $A' = \uparrow^{\mathcal{B}
  (\mathfrak{L})} A$ it is obvious that this is an order embedding.
\end{proof}

\section{Postface}

Pointfree funcoids are a \textbf{massive} generalization of locales and
frames: They don't only require the lattice of filters to be boolean but these
can be even not lattices of filters at all but just arbitrary posets. I think
a new era in pointfree topology starts.

Much work is yet needed to relate different properties of frames and locales
with corresponding properties of pointfree funcoids.