\chapter{More on connectedness}

\emph{This section is a very rough draft.}

\begin{prop}
  There are filters $\mathcal{A}$, $\mathcal{B}$, such that there are no
  filters $\mathcal{X} \sqsubseteq \mathcal{A}$, $\mathcal{Y} \sqsubseteq
  \mathcal{B}$ such that $\mathcal{X} \sqcup \mathcal{Y} = \mathcal{A} \sqcup
  \mathcal{B}$ and $\mathcal{X} \asymp \mathcal{Y}$.
\end{prop}

\begin{proof}
  \url{https://math.stackexchange.com/questions/2639206}

  (It also follows that sometimes $Z (D a)$ is not a complete lattice, because
  otherwise we could prove this theorem.)
\end{proof}

\begin{prop}
  If $\mathcal{A}$, $\mathcal{B}$ are filters and $\mathcal{A} \sqcup
  \mathcal{B} = U$ is principal filter, then there are sets $X \sqsubseteq
  \mathcal{A}$, $Y \sqsubseteq \mathcal{B}$ such that $X \sqcup Y = U$ and $X
  \asymp Y$.
\end{prop}

\begin{proof}
  Take $X = \Cor \mathcal{A}$ and $Y' = \Cor \mathcal{B}$. Then $X
  \sqcup Y' = U$ because of co-separability of $\mathfrak{F} (U)$. Take $Y = U
  \setminus X$. Then $X \sqcup Y = U$ and $X \asymp Y$.
\end{proof}

\begin{prop}
  A principal filter $A$ is connected regarding endofuncoid $\mu$ iff
  \[ \forall X, Y \in \mathscr{P} (\Ob \mu) \setminus \{ \bot \} :
     \left( X \sqcup Y = A \wedge X \asymp Y \Rightarrow X \mathrel{[\mu]} Y
     \right) . \]
\end{prop}

\begin{proof}
  Easily follows from ??.
\end{proof}

\begin{defn}
  \emph{Connected component} of a filter regarding a funcoid is a maximal
  connected subfilter of this filter.
\end{defn}

TODO: For reloids too.

Subfilter of a connected filter is connected.

\begin{prop}
  If $U$ is a principal filter, then it is connected regarding $\mu$ iff it is
  connected regarding $S (\mu)$.
\end{prop}

\begin{proof}
  If $U$ is connected regarding $\mu$, it is connected regarding $S (\mu)$,
  obviously.

  Suppose $U$ is connected regarding $S (\mu)$. Then for $X, Y \in \mathscr{P}
  (\Ob \mu) \setminus \{ \bot \}$ we have if $X \sqcup Y = U$ and $X
  \asymp Y$, then $X \mathrel{[S (\mu)]} Y$. So $X \times Y \nasymp 1 \sqcup
  \mu \sqcup \mu^2 \sqcup \ldots$ and thus by distributivity for principal
  filter we have $X \times Y \nasymp \mu^n$ for some $n \geq ? ?$ that is $X
  \mathrel{[\mu^n]} Y$ for some $n$ and thus there are atomic filters $p_0,
  \ldots, p_n$ such that $p_0 \in \atoms^{\mathfrak{F}} X$, $p_n \in
  \atoms^{\mathfrak{F}} Y$ and $p_i \mathrel{[\mu]} p_{i + 1}$. Thus
  there is $k$ such that $p_k \mathrel{[\mu]} p_{k + 1}$ and $p_k \in
  \atoms^{\mathfrak{F}} X$, $p_{k + 1} \in \atoms^{\mathfrak{F}}
  Y$. Thus $X \mathrel{[\mu]} Y$. We have $U$ connected regarding $\mu$.
\end{proof}

Also for $S^{\ast}$

\begin{prop}
  If two connected components have non-least meet, then their join is
  connected.
\end{prop}

\begin{proof}
  ??
\end{proof}

\begin{prop}
  Connected components do not intersect.
\end{prop}

\begin{proof}
  Let $\mathcal{A}$, $\mathcal{B}$ be distinct connected components of a
  filter $\mathcal{F}$ regarding funcoid $\mu$. Suppose they intersect, that
  is $\mathcal{A} \sqcap \mathcal{B} \neq \bot$. Without loss of generality
  assume $\mathcal{A} \nsqsubseteq \mathcal{B}$. So (theorem
  ??) there exists $x \in \atoms \mathcal{A}$ and $x \asymp
  \mathcal{B}$.

  By definition of connectedness of $\mathcal{A}$, we have $x \mathrel{[\mu]}
  \mathcal{A} \sqcap \mathcal{B}$ and therefore $x \mathrel{[\mu]}
  \mathcal{B}$.

  ??
\end{proof}

\begin{example}
  Connected components may not form a weak partition.
\end{example}

\begin{proof}
  Consider funcoids $\Delta \times^{\mathsf{FCD}} \Delta$ on real line.
  Then connected components are (prove!) non-zero singletons and $\Delta$. It
  is not a weak partition.
\end{proof}

Add more counter-examples (for non-principal filters).
