\documentclass[english,reqno,12pt]{amsbook}
\usepackage[paperwidth=5.06in, paperheight=7.81in]{geometry}
\usepackage[T1]{fontenc}
\synctex=-1
% \usepackage{xcolor}
% \usepackage{hyperref}
\usepackage{babel}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{agt}
\makeindex
% \usepackage[all]{xy}
% \usepackage[unicode=true,
%  bookmarks=true,bookmarksnumbered=true,bookmarksopen=false,
%  breaklinks=false,pdfborder={0 0 0},backref=false,colorlinks=true]
%  {hyperref}
\hypersetup{pdftitle={Algebraic General Topology. Book 3: Algebra. Edition 3},
 pdfauthor={Victor Porton},
 pdfsubject={general topology, algebra},
 pdfkeywords={algebraic general topology,quasi-uniform spaces,generalizations of proximity spaces,generalizations of nearness spaces,generalizations of uniform spaces,generalizations of metric spaces,ordered semigroups,ordered monoids,abstract algebra,universal algebra}}

\usepackage{xr,refcount}
\externaldocument[book-]{volume-1}
\newcommand{\bookref}[1]{\ref*{book-#1}}

% Continue numbering of book.pdf
\setcounter{thm}{\getrefnumber{book-finalthm}}
\addtocounter{thm}{-1}

\begin{document}

\title{Algebraic General Topology.\\Book 3: Algebra.\\Edition 3}

\author{Victor Porton}

\email{\href{mailto:porton@narod.ru}{porton@narod.ru}}

\urladdr{\href{http://www.mathematics21.org}{http://www.mathematics21.org}}

\date{\today}

\begin{abstract}
I define \emph{space} as an element of an ordered semigroup action, that is a semigroup action conforming to a partial order. Topological spaces, uniform spaces, proximity spaces, (directed) graphs, metric spaces, etc.\ all are spaces. It can be further generalized to ordered precategory actions (that I call \emph{interspaces}). I build basic general topology (continuity, limit, openness, closedness, hausdorffness, compactness, etc.)\ in an arbitrary space. Now general topology is an algebraic theory.

For example, my generalized continuous function are: continuous function for topological spaces, proximally continuous functions for proximity spaces, uniformly continuous functions for uniform spaces, contractions for metric spaces, discretely continuous functions for (directed) graphs.

Was a spell laid onto Earth mathematicians not to find the most important structure in general topology until 2019?
\end{abstract}


\keywords{algebraic general topology, quasi-uniform spaces, generalizations of proximity spaces, generalizations of nearness spaces, generalizations
of uniform spaces, ordered semigroups, ordered monoids, abstract algebra, universal algebra}


\subjclass[2010]{06F05, 06F99, 08A99, 20M30, 20M99, 54J05, 54A05, 54D99, 54E05, 54E15, 54E17, 54E99, 51F99, 54E25, 30L99, 54E35}

\maketitle

\tableofcontents{}

This is a draft.

It is a continuation of \cite{volume-1}.

You can read this text without any knowledge of algebraic general topology~(\cite{volume-1}). But to have some examples of how to apply this theory, you need to know what funcoids and reloids are and how funcoids are related with topological spaces.

\include{chap-osgroups}

% \printindex{}

\bibliographystyle{plain}
\bibliography{refs}

\end{document}
